### 2017-10-23 paper/sections/1_introduction.tex
paper: fill in all CITEMEs, hammer on main points
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: tone down HPCness and simplify captions
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC have scalability problems because
administrative tasks, like checkpointing~\cite{bent_plfs_2009} or scanning the
file system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current trends in HPC, where architectures are transitioning from complex
storage stacks with burst buffer, file system, object store, and tape tiers to
more simplified stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}; this puts more pressure on data access
because more requests end up hitting the same layer and latencies cannot be
hidden while data migrates across tiers.

% What is HPC doing?
To address this, developers are relaxing the consistency and durability
semantics in the file system because weaker guarantees are sufficient for their
applications. For example, many batch style jobs do not need the strong
consistency that the file system provides, so
BatchFS~\cite{zheng:pdsw2014-batchfs} and DeltaFS~\cite{zheng:pdsw2015-deltafs}
do more client-side processing and merge updates when the job is done. HPC
developers are turning to these non-POSIX IO solutions because their applications
are well-understood ({\it e.g.}, well-defined read/write phases,
synchronization only needed during certain phases, workflows describing
computation, etc.) and because these applications wreak havoc on file systems designed for
general-purpose workloads ({\it e.g.}, checkpoint-restart's N:N and N:1 create
patterns~\cite{bent_plfs_2009}).

\begin{figure}[tb]
\centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{ Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients can relax consistency on their
subtree (HDFS) or even decouple the subtree and move it locally (BatchFS,
RAMDisk). Decoupled subtrees can further relax durability for even better
performance.  Clients that require stronger guarantees (POSIX IO) can still reside
in the same namespace.  }\label{fig:subtree-policies}
\end{figure}

>>>>

% What is the problem?
File system metadata services in HPC and data center applications  have
scalability problems because administrative tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current trends; for example, HPC architectures are transitioning from
complex storage stacks with burst buffer, file system, object store, and tape
tiers to more simplified stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put more pressure
on data access because more requests end up hitting the same layer and
latencies cannot be hidden while data migrates across tiers.

% What is HPC doing?
To address this, developers are relaxing the consistency and durability
semantics in the file system because weaker guarantees are sufficient for their
applications. For example, many batch style jobs do not need the strong
consistency that the file system provides, so
BatchFS~\cite{zheng:pdsw2014-batchfs} and DeltaFS~\cite{zheng:pdsw2015-deltafs}
do more client-side processing and merge updates when the job is done.
Developers in these domains are turning to these non-POSIX IO solutions because
their applications are well-understood ({\it e.g.}, well-defined read/write
phases, synchronization only needed during certain phases, workflows describing
computation, etc.) and because these applications wreak havoc on file systems
designed for general-purpose workloads ({\it e.g.}, checkpoint-restart's N:N
and N:1 create patterns~\cite{bent_plfs_2009}).

\begin{figure}[tb] \centering
\includegraphics[width=0.35\textwidth]{figures/subtree-policies1.png}
\caption{Illustration of subtrees with different semantics co-existing in a
global namespace.  For performance, clients can relax consistency on their
subtree (HDFS) or decouple the subtree and move it locally (BatchFS, RAMDisk).
Decoupled subtrees can relax durability for even better performance.
}\label{fig:subtree-policies} \end{figure}

### 2017-10-23 paper/sections/3_posix_overheads.tex
paper: tone down HPCness and simplify captions
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: a journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large
(on the order of MBs) which ensures (1) sequential writes into the object store
and (2) the ability for daemons to trim redundant or irrelevant journal
entries.  The journal is striped over objects where multiple journal updates
can reside on the same object. There are two tunables for controlling the
journal: the segment size and the number of segments that can be written in
parallel. Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

@@

\textbf{CephFS Design}: capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, creating and updating inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

>>>>

% - sequential IO, trim redundant operations
\textbf{CephFS Design}: A journal of metadata updates that streams into the
resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to be large
(on the order of MBs) which ensures (1) sequential writes into the object store
and (2) the ability for daemons to trim redundant or irrelevant journal
entries.  The journal is striped over objects where multiple journal updates
can reside on the same object. There are two tunables for controlling the
journal: the segment size and the number of segments that can be written in
parallel. Unless the journal saturates memory or CPU resources, larger values
for these tunables results in better performance.

@@

\textbf{CephFS Design}: Capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, creating and updating inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

### 2017-10-23 paper/sections/4_methodology.tex
paper: ken edits
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: tone down HPCness and simplify captions
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/fig-decouple.png}
\caption{Applications decouple the namespace, write updates to a local journal,
and delay updates using the \textbf{mechanisms} shown here; they are described
in Table~\ref{table:mechanisms}.}\label{fig:decouple}
\end{figure}

\begin{table}
\begin{tabular}{ r | l }
  Mechanism         & Description \\\hline
  RPCs              & round trip remote procedure calls \\
  Stream            & stream journal into object store \\
  Append Client Journal & events appended to in-memory journal \\
  Volatile Apply & apply to metadata store in memory \\
  Nonvolatile Apply    & apply to metadata store in obj store \\
  Local Persist     & journal saved to client's disk \\
  Global Persist    & journal saved in object store \\
\end{tabular}
\caption{Mechanisms are composed together to form consistency and
durability semantics.\label{table:mechanisms}} 
\end{table}

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability~\footnote{This is the
normal case.  IndexFS also has bulk merge which would transition the system
into ``weak consistency"}; DeltaFS uses ``invisible" consistency and ``local"
durability and BatchFS uses ``weak" consistency and ``local" durability. These
systems have other features that could push them into different semantics but
we assign labels here based on the points emphasized in the papers.  To compose
the mechanisms users inject which mechanisms to run and which to use in
parallel using a domain specific language.  Although we can achieve all
permutations of the different guarantees in Table~\ref{table:spectrum}, not all
of them make sense. For example, it makes little sense to do \texttt{append
client journal+RPCs} since both mechanisms do the same thing or
\texttt{stream+save} since ``global" durability is stronger and has more
overhead than ``local" durability. The cost of each mechanism and the semantics
described above are quantified in Sections~\S\ref{sec:microbenchmarks}
and~\S\ref{sec:use-case-1}.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/fig-decouple.png}
\caption{Illustration of the \textbf{mechanisms} used by applications to build
consistency/durability semantics. Descriptions are provided in
Table~\ref{table:mechanisms} and the underlined words in
Section~\S\ref{sec:the-cudelesfs-mechanisms}.}\label{fig:decouple}
\end{figure}

\begin{table}
\begin{tabular}{ r | l }
  Mechanism         & Description \\\hline
  RPCs              & round trip remote procedure calls \\
  Stream            & stream journal into object store \\
  Append Client Journal & events appended to in-memory journal \\
  Volatile Apply & apply to metadata store in memory \\
  Nonvolatile Apply    & apply to metadata store in obj store \\
  Local Persist     & journal saved to client's disk \\
  Global Persist    & journal saved in object store \\
\end{tabular}
\caption{Descriptions of the mechanisms. Example compositions are shown in Table~\ref{table:spectrum}.\label{table:mechanisms}} 
\end{table}

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} (we construct the semantics for these systems later
in Section~\S\ref{sec:microbenchmarks}).  POSIX IO-compliant systems like
CephFS and IndexFS have global consistency and durability~\footnote{This is the
normal case.  IndexFS also has bulk merge which would transition the system
into ``weak consistency"}; DeltaFS uses ``invisible" consistency and ``local"
durability and BatchFS uses ``weak" consistency and ``local" durability. These
systems have other features that could push them into different semantics but
we assign labels here based on the points emphasized in the papers.  To compose
the mechanisms users inject which mechanisms to run and which to use in
parallel using a domain specific language.  Although we can achieve all
permutations of the different guarantees in Table~\ref{table:spectrum}, not all
of them make sense. For example, it makes little sense to do \texttt{append
client journal+RPCs} since both mechanisms do the same thing or
\texttt{stream+local persist} since ``global" durability is stronger and has more
overhead than ``local" durability. The cost of each mechanism and the semantics
described above are quantified in Sections~\S\ref{sec:microbenchmarks}
and~\S\ref{sec:use-case-1}.

### 2017-10-23 paper/sections/6_results.tex
paper: tone down HPCness and simplify captions
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{Performance of each mechanism (left) and building
consistency/durability guarantees (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.  \label{fig:composable-mechanisms}}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{The performance and features of Cudele. (a) shows the cost of
merging client journals at the metadata server. Merging is better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. In (b), the allow/block API isolates directories from interfering
clients. (c) is the slowdown of a single client syncing updates to the global
namespace. The inflection point is the trade-off of frequent updates vs. larger
journal files.\label{fig:use-cases}}
\end{figure*}

>>>>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{Performance of each mechanism (left) and building the
consistency/durability semantics of real-world systems (right) for 100K files
creates from a single client. Results are normalized to the runtime of writing
events to the client's in-memory journal.  \label{fig:composable-mechanisms}}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Use Case 2}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Use Case 3}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{The performance and features of Cudele. (a) shows the cost of
merging client journals at the metadata server. Shipping and merging journals of updates scales better than RPCs
because there are less messages and consistency/durability code paths are
bypassed. In (b), the allow/block API isolates directories from interfering
clients. (c) is the slowdown of a single client syncing updates to the global
namespace. The inflection point is the trade-off of frequent updates vs. larger
journal files.\label{fig:use-cases}}
\end{figure*}
